%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Consultant} % Job title
    {McKinsey} % Organization
    {Gurgaon} % Location
    {Oct. 2017 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Breaking down blocks of code, creating solutions for testing, and eating pizza every now and then.Prepare an automated BDD-driven Test Solution including E2E Tests using Protractor,Puppeteer,Cucumber}
        \item {Include APITests,developed using Chakram and Rest Assured,and integrate it as a part of a greater DevOps driven approach-integrating the tests with daily builds.}
        \item {Create a robust feature driven testing solution and environment for the projects and own the QA side of the project from initial design stage to deployment and release}
        \item{In conjunction with various product teams, liase the expertise of the various other QA members and create a resource-pool for QA efforts.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Software Development Engineer In Test} % Job title
    {Innotical Solutions} % Organization
    {Noida, India} % Location
    {Mar. 2017 - Sept. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created test frameworks,detected chinks in code armor for mobile and webapps.}
        \item{Created an automated CI driven Test framework for both e2e and REST API's using Postman, Protractor, Jasmine, Newman}
        \item {reated test artefacts,documents,test bed,test scenarios for creating a test platform to demonstrate conformance to all functional and UI requirements for three releases of MySwaasth Health Portal}
        \item {Mobile automation using Appium for an incident management platform–for mobile app developed in hybrid platform using React Native/Ionic.This involved multilingual
testing as well.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Calc. Automation Specialist} % Job title
    {Aon Corporation (previously Aon Hewitt} % Organization
    {Gurgaon, India} % Location
    {Nov. 2012 - Feb. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {DCreating, building and testing a backend calculation engine for Aon’s Pension System.}
        \item {Perform formal and informal analysis of the specifications,business requirements,plan provisions to prepare for various test conditions for
testing Aon’s benefit calculation system- Total Business Administration (TBA).}
        \item{Find,document and report bugs,defects,errors,interoperability flaws and other issues within the TBA for Aon’s global client base}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Freelance Software Tester} % Job title
    {99 Tests} % Organization
    {India} % Location
    {Sep. 2013, Mar. 2015 - Oct. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Participated in various testing cycles organised for Black box testing of various web apps and mobile apps - Sched LLC, BHIM UPI,EdCast }
        \item {Building Automated Solution for a football platform for live football and game streaming.}
      \end{cvitems}
      %\begin{cvsubentries}
      %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
      %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      %\end{cvsubentries}
    }

%---------------------------------------------------------
\end{cventries}
